Weight analysis

### 2022-11-11 code/Round 1/Cytokines adjusted.Rmd
Progressed

# Cytokines for experiment 1. - Tissue weight adjusted.

@@

First you load the data and check the structure. Make sure cytokine concentrations are all numeric (<dbl>). If not, mutate non-numeric columns with mutate_if(is_character).  
```{r load data, echo=FALSE}
# Import dataset
cytokines <- read_excel("data/processed/cytokines.xlsx")

tissue_weight_destribution <- cytokines %>%   # run normality test on tissue weight
  filter(tissue == "ileum") %>% 
  filter(exp_number == "1") %>% 
  group_by(group) %>% 
  shapiro_test(tissue_weight_mg)

# group  variable         statistic      p
#   <chr>  <chr>                <dbl>  <dbl>
# 1 AB-BF  tissue_weight_mg     0.917 0.404 
# 2 AB-FF  tissue_weight_mg     0.953 0.686 
# 3 CON-BF tissue_weight_mg     0.771 0.0138
# 4 CON-FF tissue_weight_mg     0.812 0.144

#look at tissue weight distribution
cytokines %>% 
  filter(tissue == "ileum") %>% 
  filter(exp_number == "1") %>% 
  ggplot(aes(x = group, y = tissue_weight_mg, fill = group)) + 
  geom_boxplot() +
  geom_point()
```
<!-- Looks fine. Go ahead and  adjust-->

```{r adjust for tissue weight , echo=FALSE}
cytokines_adjusted <- cytokines %>% 
  pivot_longer(.,
               cols = INFg:TNFa ,
               names_to = "variables",
               values_to = "values"
  ) %>% 
  mutate(
    group = recode_factor(  #Change the order of the groups to desired plot order
      group,
      "CON-BF"= "CON-BF",
      "CON-FF" = "CON-FF",
      "AB-BF"= "AB-BF",
      "AB-FF"= "AB-FF"
      )) %>% 
  mutate(values = if_else(tissue == "ileum", values/tissue_weight_mg, values)) %>% #Adjust for tissue weight
  pivot_wider(
    id_cols = c(
      sample_id,exp_number, group, received_antibiotics,maternal_treatment, tissue,tissue_weight_mg),
    names_from = variables, 
    values_from = values)

@@

```{r visualize data, eval=FALSE, include=FALSE}
#normality_check 
shapiro_failed <- cytokines_long %>% 
  filter(exp_number == 1) %>% 
  filter(tissue == "ileum") %>%
  filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  group_by(variables, group) %>% 
  shapiro_test(values) %>% 
  filter(p < 0.05)

log10_shapiro_failed <- cytokines_long %>% 
  filter(exp_number == 1) %>% 
  filter(tissue == "ileum") %>%
  filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  mutate(values = log10(values)) %>% 
  group_by(variables, group) %>% 
  shapiro_test(values) %>% 
  filter(p < 0.05)

#Density plots to show distribution of cytokines
histogram <- cytokines_long %>% 
  filter(exp_number == 1) %>% 
  filter(tissue == "ileum") %>%
  filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  ggplot(aes(x = values, fill = group)) + 
  geom_density() +
  facet_wrap(~ variables, ncol = 2,
             scales = "free")

log10_histogram <- cytokines_long %>% 
  filter(exp_number == 1) %>% 
  filter(tissue == "ileum") %>%
  filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  ggplot(aes(x = log10(values), fill = group)) + 
  geom_density() +
  facet_wrap(~ variables, ncol = 2,
             scales = "free")

#Jitter plots. Works
jitter_plot <- cytokines_long %>% 
  filter(exp_number == 1) %>% 
  filter(tissue == "ileum") %>%
  #filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  ggplot(aes(x = group, y = values, color = group)) +
  geom_jitter() +
  facet_wrap(~ variables,
             scales = "free")

log10_jitter_plot <- cytokines_long %>% 
  filter(exp_number == 1) %>% 
  filter(tissue == "ileum") %>%
  filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  mutate(adjusted_values = log10(values)) %>% 
  ggplot(aes(x = group, y = values, color = group)) +
  geom_jitter() +
  facet_wrap(~ variables,
             scales = "free") 
```

Set the tissue type to whatever tissue your data are extracted from, or that you want to analyze first.
```{r load data and set tissue type, include=FALSE}
#set tissue type
sample_tissue <- "ileum"
```

@@

A regression model of the effects of type of feed and antibiotics treatment
```{r echo=FALSE, warning=FALSE}
#### Make regression model on long format
linear_reg_model <- cytokines_long %>% 
  filter(tissue == sample_tissue) %>% 
  group_by(variables) %>% 
  do(lm(data = ., values ~ MAT+FEED+MAT*FEED) %>% tidy)  %>% filter(term!='(Intercept)')

linear_reg_model %>%  
  select(-statistic) %>% 
  kable(., caption = 'Effect of treatment factors on cytokine expression levels', digits = 3)

>>>>

# Cytokines for experiments  - Tissue weight adjusted.

```{r load packages, include=FALSE}
library(readxl) 
library(tidyverse)
library(gt)
library(gtsummary)
library(broom)
library(rstatix)
library(knitr)
library(patchwork)
library(ggpubr)
```

# Introduction to script

This script is useful for analyzing cytokine expression from MSD Mesoscale assays. It is currently optimized for the 'Pro-inflammatory Vplex 10 Mouse kit', analysing the cytokines INFg, IL_10, IL_12p70, IL_1b, IL_2, IL_4,IL_5, IL_6, KCGRO, and TNFa.

# Cytokines for experiment 2.

@@

First you load the data and check the structure. Make sure cytokine concentrations are all numeric (<dbl>). If not, mutate non-numeric columns with mutate_if(is_character).

```{r load data, echo=FALSE}
# Import dataset
cytokines <- read_excel("data/processed/cytokines.xlsx")
```

Set the tissue type and experimental round here:

```{r load data and set tissue type, include=FALSE}
#set tissue type
sample_tissue <- "ileum"
study_round <- "2"
```

```{r load data, echo=FALSE}
cytokines %>%   # run normality test on tissue weight
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  group_by(group) %>% 
  shapiro_test(tissue_weight_mg)

# group    variable         statistic      p
 # <chr>    <chr>                <dbl>  <dbl>
# CON-BF   tissue_weight_mg     0.833 0.197 
#GENTA-BF tissue_weight_mg     0.748 0.0120
#VANCO-BF tissue_weight_mg     0.833 0.0861
#look at tissue weight distribution

cytokines %>%       #Weight of tissue samples
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  ggplot(aes(x = group, y = tissue_weight_mg, fill = group)) + 
  geom_boxplot() +
  geom_point() +
  labs(
    title = "Tissue weight of intestinal samples, experiment 2"
  )
```
<!-- Looks fine. Go ahead and  adjust-->

```{r adjust for tissue weight , echo=FALSE}
cytokines_adjusted <- cytokines %>% 
  pivot_longer(.,
               cols = INFg:TNFa ,
               names_to = "variables",
               values_to = "values"
  ) %>% 
  mutate(
    group = recode_factor(  #Change the order of the groups to desired plot order
      group,
      "CON-BF"= "CON-BF",
      "CON-FF" = "CON-FF",
      "AB-BF"= "AB-BF",
      "AB-FF"= "AB-FF"
      )) %>% 
  mutate(values = if_else(tissue == "ileum", values/tissue_weight_mg, values)) %>% #Adjust for tissue weight
  pivot_wider(
    id_cols = c(
      sample_id,exp_number, group, received_antibiotics,maternal_treatment, type_of_feed, tissue,tissue_weight_mg),
    names_from = variables, 
    values_from = values)

@@

```{r visualize data, eval=FALSE, include=FALSE}
cytokines_long %>%                       #normality_check  of cytokine distributions
  filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  #filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  group_by(variables, group) %>% 
  shapiro_test(values) %>% 
  filter(p < 0.05)

#Non-normal distributions: 
#  group    variables variable statistic      p
#  <fct>    <chr>     <chr>        <dbl>  <dbl>
# VANCO-BF IL-1b     values       0.795 0.0363
# GENTA-BF IL-4      values       0.777 0.0240

#log10 transformed shapiro_test - failed variables
cytokines_long %>% 
 filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  mutate(values = log10(values)) %>% 
  group_by(variables, group) %>% 
  shapiro_test(values) %>% 
  filter(p < 0.05)

#  group    variables variable statistic       p
#  <fct>    <chr>     <chr>        <dbl>   <dbl>
# VANCO-BF IL-1b     values       0.727 0.00728     # transformation helped.

#Density plots to show distribution of cytokines
histogram <- cytokines_long %>% 
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  ggplot(aes(x = values, fill = group)) + 
  geom_density() +
  facet_wrap(~ variables, ncol = 2,
             scales = "free")

log10_histogram <- cytokines_long %>% 
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  #filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  ggplot(aes(x = log10(values), fill = group)) + 
  geom_density() +
  facet_wrap(~ variables, ncol = 2,
             scales = "free")

#Jitter plots. Works
jitter_plot <- cytokines_long %>% 
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  #filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  ggplot(aes(x = group, y = values, color = group)) +
  geom_jitter() +
  facet_wrap(~ variables,
             scales = "free")

log10_jitter_plot <- cytokines_long %>% 
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  mutate(adjusted_values = log10(values)) %>% 
  ggplot(aes(x = group, y = values, color = group)) +
  geom_jitter() +
  facet_wrap(~ variables,
             scales = "free") 
```

@@

A regression model of the effects of type of feed and antibiotics treatment
```{r echo=FALSE, warning=FALSE}
#### Make regression model on long format
linear_reg_model <- cytokines_long %>% 
  filter(tissue == sample_tissue) %>%
  filter(exp_number == study_round) %>% 
  group_by(variables) %>% 
  do(lm(data = ., values ~ maternal_treatment+type_of_feed +maternal_treatment*type_of_feed) %>% tidy)  %>% filter(term!='(Intercept)')

linear_reg_model %>%  
  select(-statistic) %>% 
  filter(p.value < 0.05) %>% 
  kable(., caption = 'Effect of treatment factors on cytokine expression levels', digits = 3)

### 2022-11-11 code/Round 2/Cytokines round 2.Rmd
Progressed

```{r load data, echo=FALSE}
# Import dataset
#cytokines <- read_excel("../../Data/RawData/cytokines_round_1_r.xlsm")
cytokines <- read_excel("../../Data/CleanData/cytokines.xlsx")
glimpse(cytokines)
```

Set the tissue type to whatever tissue your data are extracted from, or that you want to analyze first.

@@

@@

### Plots and regression models

First the data must be transformed to a long format (pivot longer). Mutate any new columns with group treatments needed for the regression model (in this case MAT and FEED (experimental factors)).

```{r long format, echo=FALSE}
cytokines_long <- cytokines %>% 
  filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  pivot_longer(.,
               cols = INFg:TNFa ,
               names_to = "variables",
               values_to = "values"
  ) %>% 
  drop_na(
    values) %>% 
  # mutate(MAT = ifelse(str_detect(group,'AB'),'AB',
  #                                 ifelse(str_detect(group,'CON'),'CON', "miss")),
  #        FEED = ifelse(str_detect(group,'FF'),'FF',
  #                                 ifelse(str_detect(group,'BF'),'BF', "miss"))) %>% 
  mutate(
    group = recode_factor(  #Change the order of the groups to desired plot order
      group,
      "CON-BF"= "CON-BF",
      "CON-FF" = "CON-FF",
      "AB-BF"= "AB-BF",
      "AB-FF"= "AB-FF"
      ))

head(cytokines_long)

```

@@

```{r plots all cytokines, warning=FALSE}
plot_all_cytokines <- cytokines_long %>%
  #filter(!variables %in% "INFg") %>%  #Exclude any cytokines not wanted in the plot
ggplot(aes(x = group, 
           y = values, 
           fill = group)) + 
  geom_boxplot() +
  facet_wrap(~variables, 
             scales = 'free', 
             nrow = 5,
             ncol = 2) +
  labs(title = "Levels of pro-inflammatory cytokines in the ileum",  # Change title, and axis names
       x = "",
       y = "Tissue conc.",
       fill = "Groups",
       caption = "Matrinem round 2") +
  theme_bw()+
  theme(                   # Change the appearance of labels
    plot.title = element_text(color="darkgrey", size=12, face="bold"),
    axis.title.y = element_text(color="darkgrey", size=10, face="bold.italic"),
    axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),  # Hide labels
    axis.text.x = element_blank(),
    legend.title = element_text(face="bold"),   
    legend.position="bottom",
    legend.background = element_rect(fill="lightgrey"), # Change legend box background color
    plot.caption = element_text(color = "darkgrey", size=5)) + 
  scale_fill_brewer(palette="Set1")

all_cytokines_patch <- plot_all_cytokines + plot_annotation (
  title = 'Cytokine expression',
   subtitle = 'All cytokines measured',
  tag_levels = 'A',
  caption = 'CON = Water, BF = Breast-Feeding, GENTA = Gentamicin,  VANCO = Vancomycin',
  theme = theme(plot.title = element_text(hjust = 0.5, size=14, face="bold"),
                plot.subtitle = element_text(hjust = 0.5, face = "bold.italic"),
                plot.caption = element_text(hjust = 0.5, size=7,face = "bold")))

>>>>

```{r load data, echo=FALSE}
# Import dataset
cytokines <- read_excel("data/processed/cytokines.xlsx")
```

Set the tissue type and experimental round here:

@@

```{r load data, echo=FALSE}
cytokines %>%   # run normality test on tissue weight
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  group_by(group) %>% 
  shapiro_test(tissue_weight_mg)

# group    variable         statistic      p
 # <chr>    <chr>                <dbl>  <dbl>
# CON-BF   tissue_weight_mg     0.833 0.197 
#GENTA-BF tissue_weight_mg     0.748 0.0120
#VANCO-BF tissue_weight_mg     0.833 0.0861
#look at tissue weight distribution

cytokines %>%       #Weight of tissue samples
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  ggplot(aes(x = group, y = tissue_weight_mg, fill = group)) + 
  geom_boxplot() +
  geom_point() +
  labs(
    title = "Tissue weight of intestinal samples, experiment 2"
  )
```
<!-- Looks fine. Go ahead and  adjust-->

```{r adjust for tissue weight , echo=FALSE}
cytokines_adjusted <- cytokines %>% 
  pivot_longer(.,
               cols = INFg:TNFa ,
               names_to = "variables",
               values_to = "values"
  ) %>% 
  mutate(
    group = recode_factor(  #Change the order of the groups to desired plot order
      group,
      "CON-BF"= "CON-BF",
      "CON-FF" = "CON-FF",
      "AB-BF"= "AB-BF",
      "AB-FF"= "AB-FF"
      )) %>% 
  mutate(values = if_else(tissue == "ileum", values/tissue_weight_mg, values)) %>% #Adjust for tissue weight
  pivot_wider(
    id_cols = c(
      sample_id,exp_number, group, received_antibiotics,maternal_treatment, tissue,tissue_weight_mg),
    names_from = variables, 
    values_from = values)

#____Pivot longer____
cytokines_long <- cytokines_adjusted %>% 
  pivot_longer(.,
               cols = INFg:TNFa ,
               names_to = "variables",
               values_to = "values"
  )
```

Check for data distribution.

```{r visualize data, eval=FALSE, include=FALSE}
cytokines_long %>%                       #normality_check  of cytokine distributions
  filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  #filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  group_by(variables, group) %>% 
  shapiro_test(values) %>% 
  filter(p < 0.05)

#Non-normal distributions: 
#  group    variables variable statistic      p
#  <fct>    <chr>     <chr>        <dbl>  <dbl>
# VANCO-BF IL-1b     values       0.795 0.0363
# GENTA-BF IL-4      values       0.777 0.0240

#log10 transformed shapiro_test - failed variables
cytokines_long %>% 
 filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  mutate(values = log10(values)) %>% 
  group_by(variables, group) %>% 
  shapiro_test(values) %>% 
  filter(p < 0.05)

#  group    variables variable statistic       p
#  <fct>    <chr>     <chr>        <dbl>   <dbl>
# VANCO-BF IL-1b     values       0.727 0.00728     # transformation helped.

#Density plots to show distribution of cytokines
histogram <- cytokines_long %>% 
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  ggplot(aes(x = values, fill = group)) + 
  geom_density() +
  facet_wrap(~ variables, ncol = 2,
             scales = "free")

log10_histogram <- cytokines_long %>% 
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  #filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  ggplot(aes(x = log10(values), fill = group)) + 
  geom_density() +
  facet_wrap(~ variables, ncol = 2,
             scales = "free")

#Jitter plots. Works
jitter_plot <- cytokines_long %>% 
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  #filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  ggplot(aes(x = group, y = values, color = group)) +
  geom_jitter() +
  facet_wrap(~ variables,
             scales = "free")

log10_jitter_plot <- cytokines_long %>% 
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  filter(variables != "INFg") %>% 
  drop_na(values) %>% 
  mutate(adjusted_values = log10(values)) %>% 
  ggplot(aes(x = group, y = values, color = group)) +
  geom_jitter() +
  facet_wrap(~ variables,
             scales = "free") 
```

@@

@@

```{r plots all cytokines, warning=FALSE}
plot_all_cytokines <- cytokines_long %>%
   filter(exp_number == study_round) %>% 
  filter(tissue == sample_tissue) %>%
  #filter(!variables %in% "INFg") %>%  #Exclude any cytokines not wanted in the plot
ggplot(aes(x = group, 
           y = values, 
           fill = group)) + 
  geom_boxplot() +
  facet_wrap(~variables, 
             scales = 'free', 
             nrow = 5,
             ncol = 2) +
  labs(title = "Levels of pro-inflammatory cytokines in the ileum",  # Change title, and axis names
       x = "",
       y = "pg/ml per mg tissue",
       fill = "Groups",
       caption = "Matrinem round 2") +
  theme_bw()+
  theme(                   # Change the appearance of labels
    plot.title = element_text(color="darkgrey", size=12, face="bold"),
    axis.title.y = element_text(color="darkgrey", size=10, face="bold.italic"),
    #axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),  # Hide labels
    axis.text.x = element_blank(),
    legend.title = element_text(face="bold"),   
    legend.position="bottom",
    legend.background = element_rect(fill="lightgrey"), # Change legend box background color
    plot.caption = element_text(color = "darkgrey", size=5)) + 
  scale_fill_brewer(palette="Set1")

all_cytokines_patch <- plot_all_cytokines + plot_annotation (
  #title = 'Cytokine expression',
   #subtitle = 'All cytokines measured',
  #tag_levels = 'A',
  caption = 'CON = Water, BF = Breast-Feeding, GENTA = Gentamicin,  VANCO = Vancomycin',
  theme = theme(plot.title = element_text(hjust = 0.5, size=14, face="bold"),
                plot.subtitle = element_text(hjust = 0.5, face = "bold.italic"),
                plot.caption = element_text(hjust = 0.5, size=7,face = "bold")))

### 2022-11-11 code/Round 2/FITC round 2.Rmd
Progressed

```{r load data, echo=FALSE}
# Import dataset
fitc <- read_excel("../../Data/CleanData/fitc.xlsx")
glimpse(fitc)
```

@@

fitc<- fitc %>% 
  rename("µg/ml" = `result_µg/ml_undiluted`)
```

```{r data distribution}
no_outliers <- fitc %>% 
  filter(exp_number == 2) %>% 
  group_by(group2) %>% 
  mutate(fitc_level = ifelse(fitc_level > 10, mean(fitc_level), fitc_level))

@@

The values will be displayed as mean + sd if normally distributed or median + IQR if not. An appropriate statistical test for differences will be performed (student-t for two, normally distributed groups, Anova for more than 2 groups, Kruskal wallis for non-normally distrubuted results.)

```{r}
tbl1 <- fitc %>% 
  filter(exp_number == study_round) %>% 
  select(group2, "µg/ml") %>% 
  tbl_summary(by = group2,
              digits = everything() ~ c(2,1,1),
              missing = "no") %>%
  add_p() %>% 
  modify_header(
    label ~ "FITC Conc.",
    stat_1 = "**CON-BF**  \n (n = {n})",
    stat_2 = "**GENTA-BF**  \n (n = {n})",
    stat_3 = "**VANCO-BF**  \n (n = {n})") %>% 
  modify_spanning_header((c("stat_1", "stat_2", "stat_3") ~ "Treatment groups (N total = {N})"))

@@

```{r long format, echo=FALSE}
fitc_long <- fitc %>% 
  filter(exp_number == study_round) %>% 
  rename(values = "µg/ml") %>% 
  drop_na(
    values) %>% 
  mutate(
    group = recode_factor(  #Change the order of the groups to desired plot order
      group,
      "CON-BF"= "CON-BF",
      "GENTA-BF" = "GENTA-BF",
      "VANCO-BF"= "VANCO-BF"
      ))

>>>>

```{r load data, echo=FALSE}
# Import dataset
fitc <- read_excel("data/processed/fitc.xlsx")
glimpse(fitc)
```

@@

fitc<- fitc %>% 
  rename(fitc_level = `result_µg/ml_undiluted`)
```

```{r data distribution}

fitc %>% 
  filter(exp_number == "2") %>% 
  drop_na(fitc_level) %>% 
  group_by(group) %>% 
  shapiro_test(fitc_level) 
#%>% filter(p < 0.05)

#Jitter plots. Works
jitter_plot <- fitc %>%
  filter(exp_number == 2) %>% 
  #filter(variables != "INFg") %>% 
  drop_na(fitc_level) %>% 
  ggplot(aes(x = group, y = fitc_level, color = group)) +
  geom_jitter()

no_outliers <- fitc %>% 
  filter(exp_number == 2) %>% 
  group_by(group2) %>% 
  mutate(fitc_level = ifelse(fitc_level > 10, mean(fitc_level), fitc_level))

@@

The values will be displayed as median + IQR. An appropriate statistical test for differences will be performed (student-t for two, normally distributed groups, Anova for more than 2 groups, Kruskal wallis for non-normally distrubuted results.)

```{r}
tbl1 <- fitc %>% 
  filter(exp_number == study_round) %>% 
  select(group2, fitc_level) %>% 
  rename("µg/mL" = fitc_level) %>% 
  tbl_summary(by = group2,
              digits = everything() ~ c(2,1,1),
              missing = "no") %>%
  add_p() %>% 
  modify_header(
    label ~ "FITC Conc.",
    stat_1 = "**CON-BF**  \n (n = {n})",
    stat_2 = "**GENTA-BF**  \n (n = {n})",
    stat_3 = "**VANCO-BF**  \n (n = {n})") %>% 
  modify_spanning_header((c("stat_1", "stat_2", "stat_3") ~ "Treatment groups (N total = {N})"))

@@

```{r long format, echo=FALSE}
fitc_long <- fitc %>% 
  filter(exp_number == study_round) %>% 
  rename(values = fitc_level) %>% 
  drop_na(
    values) %>% 
  mutate(
    group = recode_factor(  #Change the order of the groups to desired plot order
      group,
      "CON-BF"= "CON-BF",
      "GENTA-BF" = "GENTA-BF",
      "VANCO-BF"= "VANCO-BF"
      ))

### 2022-11-11 code/weight_analysis.Rmd
Progressed

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rstatix)
library(ggpubr)
library(patchwork)
```

@@

@@

#add gt table with group results

@@

```{r eval=FALSE, include=FALSE}
### Weight development during experiments   ###########

bw_development_feed <- data %>% 
filter(exp_number %in% c("1","3","4")) %>% 
filter(time %in% c("day_3", "day_5")) %>%
ggplot(aes(x = time ,
           y = bodyweight, 
           fill = type_of_feed)) +
  facet_wrap(~ exp_number + type_of_feed, 
             ncol = 2) + 
  geom_bar(stat = "identity",
           position = "dodge") + 
  guides(fill = guide_legend(title = " ")) +
  labs(
      caption = "Experimental round 2 not shown due to no formula feeding.",
    y = "Bodyweight (g)"
  ) +
  theme_bw()

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rstatix)
library(ggpubr)
library(patchwork)
library(tidyverse)
library(readxl)
library(broom)
```

@@

#_bodyweight in all experimets._
```{r}
startweight <- data %>% 
  filter(exp_number %in% c("1", "2", "3","4")) %>% 
  filter(time %in% c("day_3", "day_5")) %>%
  drop_na(bodyweight) %>% 
  group_by(exp_number, type_of_feed, maternal_treatment, group, time) %>% 
  summarise(startweight = mean(bodyweight),
            sd = sd(bodyweight))

startweight %>% 
  filter(exp_number == "2") %>% 
  arrange(time)
```

#_birthweight in exp 2_
```{r}
birthweight <- data %>% 
  filter(exp_number %in% "2") %>% 
  filter(time %in% c("day_0", "day_1", "day_2")) %>%
  drop_na(bodyweight) %>% 
  group_by(exp_number, maternal_treatment, time) %>% 
  summarise(birthweight = mean(bodyweight),
            sd = sd(bodyweight))

lm_birthweight <- data %>%  #LM for effect of gestational age on offspring birthweight. 
  filter(exp_number %in% "2") %>% 
  filter(time %in% c("day_0", "day_1", "day_2")) %>%
  drop_na(bodyweight) %>% 
  filter(time == "day_0") %>% 
  mutate(gestation_age = if_else(maternal_treatment == "CON", 21,20)) %>% 
  do(lm(bodyweight ~ gestation_age,.) %>% tidy)
lm_birthweight

data %>% # ANOVA for effect of gestational age on offspring birthweight. 
  filter(exp_number %in% "2") %>% 
  filter(time %in% c("day_0", "day_1", "day_2")) %>%
  drop_na(bodyweight) %>% 
  filter(time == "day_0") %>% 
  mutate(gestation_age = if_else(maternal_treatment == "CON", 21,20)) %>% 
  rstatix::anova_test(., bodyweight ~ gestation_age)

@@

@@

#_Weight development during experiments_
```{r eval=FALSE, include=FALSE}
bw_development_feed <- data %>% 
filter(exp_number %in% c("1","3","4")) %>% 
filter(time %in% c("day_3", "day_5")) %>%
ggplot(aes(x = time ,
           y = bodyweight, 
           fill = type_of_feed)) +
  facet_wrap(~ exp_number + type_of_feed, 
             ncol = 2) + 
  geom_bar(stat = "identity",
           position = "dodge") + 
  guides(fill = guide_legend(title = " ")) +
  labs(
      caption = "Experimental round 2 not shown due to no formula feeding.",
    y = "Bodyweight (g)"
  ) +
  theme_bw()
